\chapter{Acknowledgments}
\vspace{2cm}
\rightline{We Don’t See Things As They Are, We See Them As We Are}
\rightline{Anaïs Nin}
\vspace{2cm}
Firstly, I would like to thank my supervisors prof. Joachim Stroth and prof. Hans Rudolf Schmidt for giving me a chance to contribute to the CBM experiment and pursue my PhD in the STS group.


I want to express my deepest gratitude to Dr. Piotr Koczoń for his unwavering support and assistance throughout my doctoral research journey. Their guidance, encouragement, and expertise have been invaluable to me, and I could not have completed this project without his help. 


I would like to express my deep gratitude to Dr. Peter Zumbruch for the incredible support and guidance he provided me during my PhD studies. Peter's vast knowledge and expertise in the field were instrumental in shaping my research ideas and methodology, and his willingness to offer feedback and constructive criticism helped me to develop my work to the highest possible standard. 

I would like to thank the STS group and the Detector Laboratory team for the support and team oriented team spirit which undoubtedly helped me realize this work successfully. I want to thank the STS PhD students and Postdocs for countless hours in the laboratory and fruitful discussion that formed this thesis. I want to thank in particular Anton Lymanets for introducing me to the laboratory and showing me how to handle all the necessary equipment. Thanks to Dr. Adrian Rodriguez Rodriguez for invaluable discussions about STS electronics and help, both during weights lifting, but in the laboratory. also I am immensely grateful to Shaifali Mehta and Kshitij Agarwal for their exceptional work and steadfast commitment to our shared goals. Their collaborative efforts have been a driving force in our research and have enabled us to achieve significant milestones. 
Big thanks to Dr. Maksym Teklishyn, who was always there providing an excellent input both at work and after it. 

I also want to thank the following people for their contribution to my thesis and work: Dr. Johann Heuser, Dr. Joerg Lehnert, 

I dedicate my PhD thesis to two extraordinary women who have shaped me into the person I am today - my beloved mother and grandmother. Their unconditional love, guidance, and support have been the pillars of my life, and without them, I would not be where I am today. My mother's unwavering faith in my abilities has been a constant source of inspiration, while my grandmother's wisdom, kindness, and strength have taught me invaluable life lessons that have guided me through the toughest of times. Together, they have shown me what it means to be resilient, compassionate, and perseverant. I am forever grateful for their sacrifices and selflessness, and I dedicate this thesis to them with immense love and appreciation. 

I want to deeply thank all my close friends, that have been with me through the last four years, especially Nicolas and Gianluca for being with me at every step of my fruitful experience in Germany, for being with me in difficult moments, and also in those happy ones.

