
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{}
  \addcontentsline{toc}{section}{References}
%  \renewcommand{\bibname}{References} % change "Biblography" to "References" in LaTeX class "report"

\begin{thebibliography}{99}

\bibitem{STS-TDR} CBM Collaboration, {\em Technical Design Report for the CBM Silicon Tracking System}, GSI-Report 2013-4, 83-88, \url{http://repository.gsi.de/record/54798} 
		
\bibitem{CBM-TN-18010} O. Bertini et al., {\em Production Readiness Review for the Silicon Sensors of the CBM Silicon Tracking System}, CBM-TN-18010 (13 May 2019)

\bibitem{CBM-TN-19005} J.\,M. Heuser and the STS workgroup, {\em Description of the STS microstrip sensors for series production}, CBM-TN-19005 (21 May 2019)

%%% 3.1.1 
\bibitem{XYTER-NIM} K. Kasinski et al., {\em Characterization of the STS/MUCH-XYTER2, a 128-Channel Time and Amplitude Measurement IC for Gas and Silicon Microstrip Sensors}, Nucl. Instr. and Meth. A 908 (2018), 225-235 

%%% 3.1.2.
\bibitem{ref3-1-2-1} C.\,J.~Schmidt, simulation with {\tt AppCAD} (\url{http://www.hp.woodshot.com/}), verification by D. Soyk with {\tt Ansys} software (\url{https://www.ansys.com}) (2015)

\bibitem{ref3-1-2-2} T. Blank et al., {\em Investigation on low mass copper flex micro-cables for the STS detector}, CBM Progress Report 2016, 42-43

%%% 3.2.2
\bibitem{ref3-2-2-1} 
I. Panasenklo et al., {\em A Custom Probe Station for Testing of CBM Silicon Strip Detectors}, in: CBM Progress Report 2019 

\bibitem{ref3-2-2-2} 
E.~Lavrik, I.~Panasenko, and H.\,R.~Schmidt, {\em Optical quality assurance procedures for the STS detector}, CBM Progress Report 2017, p.~20

%%% 3.2.5
\bibitem{ref3.2.5-1} V.~Borshchov, M.~Protsenko, C.\,J.~Schmidt, C.~Simons, D.~Soyk, I.~Tymchuk and A.~Wilms, {\em  \mbox{Micro-cables} for the CBM-STS detector modules}, Document on the specifications of the micro cables, current version: 	    
File: CBM\_cables-specification\_v14-24042020.docx, CBM-TN-20003 (24 April 2020)

\bibitem{ref3.2.5-2} QA-Protocol for the aluminum micro cables used in the CBM-STS 
CBM-QA-STS 20001 (13~March~2020) 

\bibitem{ref3.2.5-3} Table of recent microcables ordered at LTU Ltd., update April 2020, File: Microcables\_V2.xlsx 

%%% 3.2.7
\bibitem{ref3.2.7-1} W. Zubrzycka and K. Kasinski, {\em Performance evaluation of the detector and ultra-light micro-cable assembly for tracking application in CBM experiment}, Proc. SPIE Vol. 10445 104454A-1, \url{https://doi.org/10.1117/12.2280946} (7 August 2017)

%%% 3.3
\bibitem{CBM-TN-18005} C.~Simons et al., {\em The assembly of the STS sensor modules at GSI}, CBM-TN-18005 (4 March 2019)

%%% 3.4.3
      \bibitem{STS-READOUT} J. Lehnert et al., {\em, GBT based readout in the CBM experiment}, J. Instrum. 12 (2017) C0206 
      \bibitem{CROB} J. Lehnert et al., {\em Development and test of the CBM Common Readout Board (CROB)}, CBM Progress report 2017, p.45
      \bibitem{GBTX} K. Wyllie et al., {\em A Gigabit Transceiver for Data Transmission in Future High Energy Physics Experiments}, Phys. Procedia 37 (2012) 1561
      \bibitem{EMUREADOUT-PRES} W. Zabolotny et al., \url{https://indico.gsi.de/event/7101/contributions/32163/attachments/23180/29066/WUT_FPGA_DAQ.pdf}
      \bibitem{TRENZ} Trenz Electronic, {\em TE0712 TRM}, \url{https://wiki.trenz-electronic.de/display/PD/TE0712+TRM}

%%% 3.4.4

			\bibitem{CBM-QA-STS-20002} B. Schmitt and Andrea Wilms, {\em Software documentation of the
Connectivity Test via Testfan Version 1.3 used for QA purposes of the CBM-STS Chipcables}, QA Note CBM-QA-STS 20002 (26~May~2020)
			\bibitem{CBM-QA-STS-20003} A. Wilms and H. Al-Turany, {\em Software documentation of the
Vendor Data Extraction Tool Version 1.0 used as part of the CBM-STS QA-Data-Logistics}, QA Note CBM-QA-STS 20003 (26~May~2020)
      \bibitem{SW-GUI-EL} E. Lavrik, private communication 


%%% 4.1
	\bibitem{latn} U.~Frankenfeld et al., {\em STS Ladder Assembly}, CBM-TN-18011	(29 November 2018)
	\bibitem{la2018} S. Mehta et al., {\em STS ladder assembly}, CBM Progress report 2018, p.26
	\bibitem{lajinr}V. Elsha et al., {\em Design of an STS ladder assembly device}, CBM Progress report 2017, p.40
	\bibitem{cftn} J.~Heuser et al., {\em Production Readiness Review for the STS Carbon Fiber Ladders}, CBM-TN-19006	(12 June 2019)

%%% 4.2 
\bibitem{Lavrik:2018qnx}
	E.~Lavrik, U.~Frankenfeld, S.~Mehta, I.~Panasenko and H.~Schmidt,
	``High-precision contactless optical 3D-metrology of silicon sensors,''
	Nucl.\ Instrum.\ Meth.\ A \textbf{935}, 167-172 (2019)
	\url{doi:10.1016/j.nima.2019.04.039}
	[arXiv:1812.00917 [physics.ins-det]].

%%% 6.2 
\bibitem{noise_cbm} 
Weronika Zubrzycka, Krzysztof Kasinski. 
\textit{Noise considerations for the STS/MUCH readout ASIC}. 
2018 CBM Progress Report 2017, ed. I. Selyuzhenkov, A. Toya, GSI, pp.34-35.

\bibitem{smx_manual} 
Krzysztof Kasinski, et al., 
\textit{SMX2.2 Manual}, \url{https://cbm-wiki.gsi.de/foswiki/bin/view/CBMXYTER/}

\bibitem{leakage_induced} 
Weronika Zubrzycka, Krzysztof Kasinski. 
\textit{Leakage current-induced effects in the silicon microstrip and gas electron multiplier readout chain and their compensation method }, 
2018 JINST 13 T04003, \url{https://doi.org/10.1088/1748-0221/13/04/T04003}

\bibitem{flexible_csa} 
Krzysztof Kasinski, Rafal Kleczek. 
\textit{A Flexible, Low-noise Charge-sensitive Amplifier for Particle Tracking Application }, 2016 MIXDES - 23rd International Conference Mixed Design of Integrated Circuits and Systems, Lodz, 2016, pp. 124-129 

\bibitem{smx_foswiki}
\textit{CBM FOSWIKI page on IC for STS}, \url{https://cbm-wiki.gsi.de/foswiki/bin/view/CBMXYTER/}

%%% 6.3
\bibitem{ref:smallprecisiontools} 
\url{http://www.smallprecisiontools.com}

%%% 6.4
\bibitem{SMX-ref} K. Kasinski, A. Rodriguez-Rodriguez, J. Lehnert, W. Zubrzycka, R. Szczygiel, P. Otfinowski, \mbox{C.\,J.~Schmidt}, {\em Characterization of the STS/MUCH-XYTER2, a 128-channel time and amplitude measurement IC for gas and silicon microstrip sensors}, Nucl. Instr. Meth. Phys. Res. A 908 225–235 (2018),  \url{https://doi.org/10.1016/j.nima.2018.08.076}

\bibitem{FEAST-ref} S. Michelis et al., CERN, \url{https://project-dcdc.web.cern.ch/projectdcdc/
public/Documents/FEASTMod-Datasheet.pdf}

\bibitem{GBTx-ref} 
P. Leitao, S. Feger, D. Porret, S. Baron, K. Wyllie, M. Barros Marin, D. Figueiredo, R. Francisco, J.\,C. Da Silva, T. Grassi, {\em Test bench development for the radiation Hard GBTX ASIC}, Journal of Instrumentation, Vol. 10, Jan 2015, TWEPP2014

\bibitem{LDO-ref}  {\em Radiation Hardened Low Drop-Out Voltage Regulator (LDO) - 1.8~V / 1.6~A}, Pre-Production Technical Interface Document, March 2019, Semi-Conductor Laboratory, Department of Space, Government of India, S.A.S. Nagar, Punjab-160071

\bibitem{WAGO-ref}  \url{https://www.wago.com/de/leiterplattenanschluss/smd-leiterplattenklemme-im-gurt/p/2059-301_998-403}
	
\bibitem{SUMIDA-ref}  \url{https://sumida-flexcon.com/de-de/jumper/flexible-board-connections/panta-fixpower/konfigurator/}


%%% 6.8
\bibitem{ref6-8-1} T. Blank et al., {\em Investigation on low mass copper flex micro-cables for the STS detector}, CBM Progress Report 2016, ISBN 978-3-9815227-4-7

\bibitem{ref6-8-2}T. Blank et al., {\em High density flex-cable and interconnection technologies for large silicon detector modules}, International Conference on Electronics Packaging and iMAPS All Asia Conference (ICEP-IAAC), \url{DOI:10.23919/ICEP.2018.8374306}



%%% 7.2
\bibitem{ref7-2-1} CBM Collaboration, {\em Technical Design Report for the CBM Silicon Tracking System}, GSI-Report 2013-4, 83-88, \url{http://repository.gsi.de/record/54798}

\bibitem{ref7-2-2}	C. Simons, this note,  Sect.~\ref{sec:assembly} {\em Assembly Tools and Workflow}

\bibitem{ref7-2-3}	T. Blank et al., this note, Sect.~\ref{sec:copper} {\em Copper-based Micro-Cables\\}

\bibitem{ref7-2-4}	P. Pfistner et al., CBM Progress Report 2018, p. 19, \url{http://repository.gsi.de/record/220128}


%%% 7.3
	\bibitem{BMN-TDR} BM@N STS group, {\em Technical Design Report for the Silicon Tracking System as part of the hybrid tracker of the BM@N experiment}, December 2019, \url{https://bmn-wiki.jinr.ru/bin/view/Doc}
	
	\bibitem{bonding-test} N. Sukhov, D. Dementev, M. Dogan, A. Kolozhvari et al. {\em Development of bonding quality control for assembly of the silicon microstrip sensor modules}, CBM Progress report 2018, p.~18
	
\end{thebibliography} 





  
